---
title: "CAF Analysis"
author: "J.Damrauer"
date: "2023-12-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r Loading libraries, echo=FALSE, message=FALSE,warning=FALSE}
library(ggplot2)
library(ggpubr)
library(tidyr)
library(stats)
library(forcats)
library(plyr)
library(stats)
library(reshape2)
library(plyr)
library(dplyr)
library(survival)
library(survminer)
library(ComplexHeatmap)
library(circlize)
library(tidyverse)
library(rstatix)
library(ggpubr)
library(GGally)
library(ggfortify)
library(gridExtra)
library(rstatix)
library(ggcorrplot)
library(impute)
library(fgsea)
library(ggVennDiagram)
```

# Correlation between CAF subtypes and RCC/BCa features
**CIBERSORTx data was generated in w/ 500 permuations [QN disabled]


## UROMOL

<https://www.nature.com/articles/s41467-021-22465-w>

URMOL is a Non-muscle invasive cohort and proposed a NMIBC subtyping scheme Class 1 [FGFR3 mutant], Class 2a [TP53 mutant and aggressive], Class 2b [TP53 mutant, EMT, immune high] and Class 3[FGFR3 mutant, immune low].

```{r Comparison Plots - UROMOL, echo=FALSE,message=FALSE, warning=FALSE}

UROMOL<-read.table("DataOutput/UROMOL.CAF.txt", sep="\t", header=T, row.names=1) %>%
subset(!(Staging %in% "CIS"))

factor(TCGA.1$Consensus, levels=c("Ba/Sq", "Stroma-rich", "LumP", "LumU", "LumNS", "NE-like"))

UROMOL.Count.Consensus<-UROMOL %>%
    subset(Consensus %in% c("Ba/Sq", "Stroma-rich", "LumP", "LumU", "LumNS", "NE-like")) %>%
  dplyr::count(Consensus, DeCAF)

UROMOL.Consensus.stats<-chisq_test(UROMOL$DeCAF, UROMOL$Consensus)

ggplot(UROMOL.Count.Consensus, aes(x=factor(Consensus, levels=c("Ba/Sq", "Stroma-rich", "LumP", "LumU", "LumNS", "NE-like")), y=n, fill=DeCAF)) +
  ggtitle("CAF subtype by Consensus Subtype")+
  theme(text = element_text(size = 12), axis.text.x = element_text(angle = 45, hjust=1))+
  geom_bar(position="fill", stat = "identity")+
  ylab("patients")+
  xlab("")+
 geom_text(aes(label = paste0(n)), position = position_fill(vjust = 0.5),
            col="black", size=3)+
      geom_signif(annotations =paste("Chi-Square p =",UROMOL.Consensus.stats$p), y_position = 1.05,
              tip_length = 0,xmin="Ba/Sq", xmax="LumNS")

ggplot(UROMOL, aes(x=factor(Consensus, levels=c("Ba/Sq", "Stroma-rich", "LumP", "LumU", "LumNS", "NE-like")), y=DeCAF.prob)) + 
  ggtitle("DeCAF_score")+
  labs(x="", y="DeCAF_score")+
  geom_boxplot(outlier.shape = NA, lwd=1)+
  theme_classic(base_size=15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  geom_jitter(aes(color=DeCAF), shape=16, fill="gray", alpha=.75, size=3, position=position_jitter(0.2), na.rm=TRUE)+
  stat_compare_means()


UROMOL.Count.Staging<-UROMOL %>%
    subset(Staging %in% c("LG-Ta","LG-T1", "HG-Ta", "HG-T1")) %>%
  dplyr::count(Staging, DeCAF)

UROMOL.Staging.stats<-chisq_test(UROMOL$DeCAF, UROMOL$Staging)

ggplot(UROMOL.Count.Staging, aes(x=factor(Staging, levels=c("LG-Ta","LG-T1", "HG-Ta", "HG-T1")), y=n, fill=DeCAF)) +
  ggtitle("CAF subtype by Grade and Stage")+
  theme(text = element_text(size = 12), axis.text.x = element_text(angle = 45, hjust=1))+
  geom_bar(position="fill", stat = "identity")+
  ylab("patients")+
  xlab("")+
 geom_text(aes(label = paste0(n)), position = position_fill(vjust = 0.5),
            col="black", size=3)+
      geom_signif(annotations =paste("Chi-Square p =",UROMOL.UROMOL.stats$p), y_position = 1.05,
              tip_length = 0,xmin="LG-Ta", xmax="HG-T1")

ggplot(UROMOL, aes(x=factor(Staging, levels=c("LG-Ta","LG-T1", "HG-Ta", "HG-T1")), y=DeCAF.prob)) + 
  ggtitle("DeCAF_score")+
  labs(x="", y="DeCAF_score")+
  geom_boxplot(outlier.shape = NA, lwd=1)+
  theme_classic(base_size=15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  geom_jitter(aes(color=DeCAF), shape=16, fill="gray", alpha=.75, size=3, position=position_jitter(0.2), na.rm=TRUE)+
  stat_compare_means()


UROMOL.Count.UROMOL<-UROMOL %>%
    subset(UROMOL %in% c("Class 1", "Class 2a", "Class 2b", "Class 3")) %>%
  dplyr::count(UROMOL, DeCAF)

UROMOL.UROMOL.stats<-chisq_test(UROMOL$DeCAF, UROMOL$UROMOL)

ggplot(UROMOL.Count.UROMOL, aes(x=UROMOL, y=n, fill=DeCAF)) +
  ggtitle("CAF subtype by UROMOL Subtype")+
  theme(text = element_text(size = 12), axis.text.x = element_text(angle = 45, hjust=1))+
  geom_bar(position="fill", stat = "identity")+
  ylab("patients")+
  xlab("")+
 geom_text(aes(label = paste0(n)), position = position_fill(vjust = 0.5),
            col="black", size=3)+
      geom_signif(annotations =paste("Chi-Square p =",UROMOL.UROMOL.stats$p), y_position = 1.05,
              tip_length = 0,xmin="Class 1", xmax="Class 3")

ggplot(UROMOL, aes(x=UROMOL, y=DeCAF.prob)) + 
  ggtitle("DeCAF_score")+
  labs(x="", y="DeCAF_score")+
  geom_boxplot(outlier.shape = NA, lwd=1)+
  theme_classic(base_size=15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  geom_jitter(aes(color=DeCAF), shape=16, fill="gray", alpha=.75, size=3, position=position_jitter(0.2), na.rm=TRUE)+
  stat_compare_means()



fit<- survfit(Surv(Prog.Time, Progression) ~DeCAF , data=UROMOL)
ggsurvplot(fit, UROMOL,
                 pval = TRUE,
           risk.table = TRUE,
                 surv.median.line = "hv",
           legend.labs = c("permCAF", "restCAF"),
                 legend.title=("CAF Subtype"),
           title="UROMOL: Progression Free Survival", 
           short.panel.labs=TRUE,
                 ggtheme = theme_bw())

fit<- survfit(Surv(Prog.Time, Progression) ~grade , data=UROMOL)
ggsurvplot(fit, UROMOL,
                 pval = TRUE,
           risk.table = TRUE,
                 surv.median.line = "hv",
            legend.labs =c("Strong permCAF", "Likely permCAF", "Lean permCAF",
                                            "Lean restCAF", "Likely restCAF", "Strong restCAF"),
                  legend.title=("CAF Subtype"),
            title="UROMOL: Progression Free Survival", 
                 short.panel.labs=TRUE,
                 ggtheme = theme_bw())

ggforest(coxph(Surv(Prog.Time, Progression) ~DeCAF + UROMOL, data=UROMOL), main="UROMOL: Progression Free Survival")

```

## TCGA

[https://linkinghub.elsevier.com/retrieve/pii/S0092-8674(17)31056-5](https://linkinghub.elsevier.com/retrieve/pii/S0092-8674(17)31056-5){.uri}

Data from the 2017 TCGA marker paper on muscle invasive bladder cancer (pre-IO approval)
Metastatic patients were removed (only M=0 patients are in the anlaysis)

```{r Comparison Plots - TCGA, echo=FALSE,message=FALSE, warning=FALSE}

TCGA<-read.table("New.TCGA.Survival.txt", sep="\t", header=T, row.names=1)

TCGA.1<-TCGA %>%
  subset(M_stage %in% c("M0"))

TCGA.Count.Consensus<-TCGA.1 %>%
  dplyr::count(Consensus, DeCAF)

TCGA.Consensus.stats<-chisq_test(TCGA.1$DeCAF, TCGA.1$Consensus)
 
ggplot(TCGA.Count.Consensus, aes(x=factor(TCGA.Count.Consensus$Consensus, levels=c("Ba/Sq", "Stroma-rich", "LumP", "LumU", "LumNS", "NE-like")), y=n, fill=DeCAF)) +
  ggtitle("CAF subtype by Consensus Subtype")+
  theme(text = element_text(size = 12), axis.text.x = element_text(angle = 45, hjust=1))+
  geom_bar(position="fill", stat = "identity")+
  ylab("patients")+
  xlab("TCGA Tumors")+
 geom_text(aes(label = paste0(n)), position = position_fill(vjust = 0.5),
            col="black", size=3)+
      geom_signif(annotations =paste("Chi-Square p =",TCGA.Consensus.stats$p), y_position = 1.05,
              tip_length = 0,xmin="Ba/Sq", xmax="LumNS")

subtype<-factor(TCGA.1$Consensus, levels=c("Ba/Sq", "Stroma-rich", "LumP", "LumU", "LumNS", "NE-like"))

ggplot(TCGA.1, aes(x=subtype, y=DeCAF.prob)) + 
  ggtitle("DeCAF_score")+
  labs(x="", y="DeCAF_score")+
  geom_boxplot(outlier.shape = NA, lwd=1)+
  theme_classic(base_size=15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  geom_jitter(aes(color=DeCAF), shape=16, fill="gray", alpha=.75, size=3, position=position_jitter(0.2), na.rm=TRUE)+
  stat_compare_means()



fit<- survfit(Surv(OS.time.5, OS.5) ~DeCAF, data=TCGA.1)

ggsurvplot(fit, TCGA.1,
                    pval = TRUE,
           risk.table = TRUE,
                 surv.median.line = "hv",
                 legend.labs = c("permCAF", "restCAF"),
                 legend.title=("CAF Subtype"),
           title="TCGA: Disease Free Survival", 
           xlab="Time (months)",
                 short.panel.labs=TRUE,
                 ggtheme = theme_bw())


fit<- survfit(Surv(OS.time.5, OS.5) ~DeCAF + UNC, data=TCGA.1)

ggsurvplot(fit, TCGA.1,
                    pval = TRUE,
           risk.table = TRUE,
                 surv.median.line = "hv",
                 legend.labs = c("permCAF:Basal", "permCAF:Luminal", "restCAF:Basal", "restCAF:Luminal"),
                 legend.title=("CAF Subtype"),
           title="TCGA: Disease Free Survival", 
           xlab="Time (months)",
                 short.panel.labs=TRUE,
                 ggtheme = theme_bw())



```

## IMvigor210

<https://www.nature.com/articles/nature25501>

Data from the phase II - IMvigor210 data. Pre-treatment metastatic UC samples from patients that went on to receive atezolizumab.

Platinum therapy subgroups -  Did patient receive platinum based chemotherapy [Y/N]. If yes, was the sample collected before or after platinum treatment.

```{r Comparison Plots - IMvigor, echo=FALSE, message=FALSE, warning=FALSE}

imvig<-read.table("DataOutput/IMvigor.CAF.20231209.txt", sep="\t", header=T, row.names=1)
IMVIG.na<-subset(IMVIG, !(is.na(binaryResponse)))

ggplot(IMVIG.na, aes(x=binaryResponse, y=DeCAF_prob)) + 
  labs(x="Best Response", y="DeCAF_prob")+
  geom_boxplot(outlier.shape = NA, lwd=1)+
  theme_classic(base_size=15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  geom_jitter(aes(color=DeCAF),shape=16, fill="gray", alpha=.75, size=3, position=position_jitter(0.2), na.rm=TRUE)+
  stat_compare_means(method="t.test")

fit<- survfit(Surv(os, censOS) ~DeCAF, data=imvig)
ggsurvplot(fit, imvig,
                    pval = TRUE,
           risk.table = TRUE,
                 surv.median.line = "hv",
                 legend.title=("CAF Subtype"),
           title="IMvigor210: Overall Survival", 
           xlab="Time (months)",
                 short.panel.labs=TRUE,
                 ggtheme = theme_bw())

ggforest(coxph(Surv(os, censOS) ~DeCAF, data=imvig))


IMVIG.Count.Consensus.stat<-chisq_test(IMVIG$DeCAF, IMVIG$Consensus)
IMVIG.Count.UNC.stat<-chisq_test(IMVIG$DeCAF, IMVIG$UNC)

ggplot(IMVIG.Count.Consensus, aes(x=factor(IMVIG.Count.Consensus$Consensus, levels=c("Ba/Sq", "Stroma-rich", "LumP", "LumU", "LumNS")), y=n, fill=DeCAF)) +
  ggtitle("CAF subtype by Consensus Subtype")+
  theme(text = element_text(size = 12), axis.text.x = element_text(angle = 45, hjust=1))+
  geom_bar(position="fill", stat = "identity")+
  ylab("patients")+
  xlab("IMvigor210 Tumors")+
 geom_text(aes(label = paste0(n)), position = position_fill(vjust = 0.5),
            col="black", size=3)+
      geom_signif(annotations =paste("Chi-Square p =",IMVIG.Count.Consensus.stat$p), y_position = 1.05,
              tip_length = 0,xmin="Ba/Sq", xmax="LumNS")


IMVIG<-imvig %>%
    subset(Consensus %in% c("Ba/Sq", "Stroma-rich", "LumP", "LumU", "LumNS"))

IMVIG.Count.Consensus<-IMVIG %>%
    subset(Consensus %in% c("Ba/Sq", "Stroma-rich", "LumP", "LumU", "LumNS")) %>%
  dplyr::count(Consensus, DeCAF)

IMVIG.Count.UNC<-IMVIG %>%
  dplyr::count(UNC, DeCAF)

subtype<-factor(IMVIG$Consensus, levels=c("Ba/Sq", "Stroma-rich", "LumP", "LumU", "LumNS", "NE-like"))

ggplot(IMVIG, aes(x=subtype, y=DeCAF_prob)) + 
  ggtitle("DeCAF_score")+
  labs(x="", y="DeCAF_score")+
  geom_boxplot(outlier.shape = NA, lwd=1)+
  theme_classic(base_size=15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  geom_jitter(aes(color=DeCAF), shape=16, fill="gray", alpha=.75, size=3, position=position_jitter(0.2), na.rm=TRUE)+
  stat_compare_means()






```


## IMmotion

<https://www.nature.com/articles/s41591-018-0053-3>

RCC treated with Sunitinib (multi-RTK inhibitor), atezolizumab (anti-PD-L1), or atezolizumab + bevacizumab (anti-VEGF)

```{r IMmotion}
rcc<-read.table("IMmotion150_CAF.txt", sep="\t", header=T, row.names=1)

rcc.atezo<-subset(rcc, ARM %in% "Atezo")

rcc.atezo<-subset(rcc.atezo, !(is.na(BestResponse.2)))

ggplot(rcc.atezo, aes(x=BestResponse.2, y=DeCAF_prob)) + 
  labs(x="Best response \natezolizumab", y="DeCAF_prob")+
  geom_boxplot(outlier.shape = NA, lwd=1)+
  theme_classic(base_size=15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  geom_jitter(aes(color=DeCAF),shape=16, fill="gray", alpha=.75, size=3, position=position_jitter(0.2), na.rm=TRUE)+
  stat_compare_means(method="t.test")


```
