---
title: "Clinical_Cleaned_Univariate"
output: html_document
date: "2023-12-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(openxlsx)
library(survival)
library(survminer)
library(dplyr)
library(gtsummary)

```

# Dataset

```{r}

dataset<-readRDS("/work/users/a/r/arthih/Laura_Clinical_Parsing/yehseq_pdac_pi.decaf_freeze_clinicalParsed_111723.rds")

```

## Data

```{r}
#PurIST with Clinical categorical

#add PurIST columns from sampInfo to clinicalDat

clinicalDat <- dataset$clinicalDatParsed

clinicalDat$sampID <- colnames(dataset$ex)

clinicalDat <- clinicalDat %>% 
  left_join(dataset$subtypeCall)

```

```{r}

clinicalDat <- clinicalDat %>% select_if(~ !all(is.na(.)))
```

```{r}

# boxplot
subset<-clinicalDat %>% 
  select(age, race, sex, pre_op_kg, pre_op_cm, pre_op_bmi, tobacco_former_current_never, tobacco_py, alcohol_yn, dmstatus_1yrdef.yes.recent.no, dmstatus_2yrdef.yes.recent.no, personal_hx_ca_yn, preop_albumin, preop_ca199, preop_ecog, preop_cholangitis_yn, chronic_pancreatitis_yn, Recent.ABX, tumor_location.clean, `Location/Procedure`, Last.Event, Path, differentiation_clean_downstaged, differentiation_clean_upstaged,`Tumor.size.(path.report,.cm).updated`, Pos.LN, T.LN, T.impute.from.TumorSize.8thEd, N.impute.from.PosLN.8thEd, Lymphovascular.Invasion.clean, PNI.clean, `Margin.(close.<1mm)`, Stage.impute.TN.8thEd, Neoadj.Tx, Neoadj.Regimen.clean, neo_folfirinox.clean, neo_GA, neo_xrt.clean, neo_other, `preop.RT.(for.adeno.only).clean`, `preop.Chemo.(for.adeno.only)`, Path.Response.score.clean, `Adj.Tx.(Yes.if.got.any.treatment.for.PDAC).clean`, `Adj.Chemo.(for.adeno.only)`, Adj_Tx.clean, `Recur.(NA.if.non-PDAC.or.non-resectable.disease,.even.if.treated.for.other.causes)`,`Recurrence.Event.(0=NED.1=radiographic.recurrence,.2.=.documented.chemical.recurrence.alone,.500=died.of.operation,.600.=.died.of.documented.non-PDAC.event.with.NED.900=unable.to.determine.due.to.lack.of.reccords,.950=unable.to.determine.due.to.indeterminate.imaging.990.=.non-resected.PDAC.case,.999=non-PDAC.case)`,`\\Recurrence.Event.(0=NED.1=radiographic.recurrence,.2.=.document\"`, Recur.Site, PurIST.prob, PurIST, PurIST.graded, DeCAF)

subset %>% select_if(is.numeric) %>% boxplot()

```

```{r}

summary <- clinicalDat %>% 
  select(age, race, sex, pre_op_kg, pre_op_cm, pre_op_bmi, tobacco_former_current_never, tobacco_py, alcohol_yn, dmstatus_1yrdef.yes.recent.no, dmstatus_2yrdef.yes.recent.no, personal_hx_ca_yn, preop_albumin, preop_ca199, preop_ecog, preop_cholangitis_yn, chronic_pancreatitis_yn, Recent.ABX, tumor_location.clean, `Location/Procedure`, Last.Event, differentiation_clean_downstaged, differentiation_clean_upstaged,`Tumor.size.(path.report,.cm).updated`, Pos.LN, T.LN, T.impute.from.TumorSize.8thEd, N.impute.from.PosLN.8thEd, Lymphovascular.Invasion.clean, PNI.clean, `Margin.(close.<1mm)`, Stage.impute.TN.8thEd, Neoadj.Tx, Neoadj.Regimen.clean, neo_folfirinox.clean, neo_GA, neo_xrt.clean, Path.Response.score.clean, `Adj.Tx.(Yes.if.got.any.treatment.for.PDAC).clean`, Adj_Tx.clean, `Recur.(NA.if.non-PDAC.or.non-resectable.disease,.even.if.treated.for.other.causes)`,`Recurrence.Event.(0=NED.1=radiographic.recurrence,.2.=.documented.chemical.recurrence.alone,.500=died.of.operation,.600.=.died.of.documented.non-PDAC.event.with.NED.900=unable.to.determine.due.to.lack.of.reccords,.950=unable.to.determine.due.to.indeterminate.imaging.990.=.non-resected.PDAC.case,.999=non-PDAC.case)`, PurIST.prob, PurIST, PurIST.graded, DeCAF) %>% 
  tbl_summary(by = DeCAF, 
              missing = "no", 
              statistic = all_continuous() ~ "{median} ({min}-{max})",
              type = list(c(chronic_pancreatitis_yn, alcohol_yn, personal_hx_ca_yn, preop_cholangitis_yn, Recent.ABX, Lymphovascular.Invasion.clean, PNI.clean, Neoadj.Tx, neo_folfirinox.clean, neo_GA,neo_xrt.clean, `Adj.Tx.(Yes.if.got.any.treatment.for.PDAC).clean`, Adj_Tx.clean,`Recur.(NA.if.non-PDAC.or.non-resectable.disease,.even.if.treated.for.other.causes)`)~'categorical'),
              digits = list(PurIST.prob~c(9,9))) %>% 
  add_p(test=list(all_continuous()~'wilcox.test',all_categorical()~'fisher.test')) %>% bold_labels()


```

```{r}

summary

```


```{r}

summary %>% as_gt %>% gt::gtsave("/work/users/a/r/arthih/Laura_Clinical_Parsing/DeCAF_Clinical_121823.html")

```

#------------------------------------------------------------------------------------
# Survival Analysis

#### clincial subset

Variables in clinicalDatParsed to be used for survival analysis (as marked in the excel by Jaewon,Jen Jen and Laura)

Using imputed T N and Stage
```{r}

data_sub <-dataset$clinicalDatParsed %>%  select(age,
                                                 pre_op_bmi,
                                                 race, 
                                                 sex, 
                                                 tobacco_former_current_never, 
                                                 alcohol_yn, 
                                                 personal_hx_ca_yn,
                                                 bileduct_stent_clean, 
                                                 preop_ca199, 
                                                 preop_cholangitis_yn,
                                                 chronic_pancreatitis_yn,
                                                 Recent.ABX, 
                                                 tumor_location.clean,
                                                 `Recur.(NA.if.non-PDAC.or.non-resectable.disease,.even.if.treated.for.other.causes)`,
                                                 Path.Response.score.clean, 
                                                 T.impute.from.TumorSize.8thEd, 
                                                 N.impute.from.PosLN.8thEd,
                                                 Pos.LN,
                                                 T.LN,
                                                 Lymphovascular.Invasion.clean, 
                                                 PNI.clean,
                                                 `Margin.(close.<1mm)`,
                                                 Date.of.Surgery,
                                                 Date.of.Dx,
                                                 Final.Date,
                                            `Overall.Survival.(diagnosis.to.death.in.months)`,
                                            `Recurrence.Event.(0=NED.1=radiographic.recurrence,.2.=.documented.chemical.recurrence.alone,.500=died.of.operation,.600.=.died.of.documented.non-PDAC.event.with.NED.900=unable.to.determine.due.to.lack.of.reccords,.950=unable.to.determine.due.to.indeterminate.imaging.990.=.non-resected.PDAC.case,.999=non-PDAC.case)`,
                                            differentiation_clean_upstaged, 
                                            differentiation_clean_downstaged,
                                            Stage.impute.TN.8thEd,
                                            Neoadj.Regimen.clean,
                                            neo_folfirinox.clean,
                                            neo_GA,
                                            neo_xrt.clean,
                                            `Adj.Tx.(Yes.if.got.any.treatment.for.PDAC).clean`,
                                            Adj_Tx.clean,
                                            `\\Recurrence.Event.(0=NED.1=radiographic.recurrence,.2.=.document\"`,
                                            Recur.Date,
                                            uniqID)

```

### Survdat

Create a dataframe to be used for survival - Survdat

```{r survdat}

## Survival

## parse clinical ---------------------------------------------------------------------
survDat <- data.frame(sampID = colnames(dataset$ex), 
                      time = dataset$clinicalDatParsed$`Overall.Survival.(OR.until.death)`,
                      event = dataset$clinicalDatParsed$Last.Event,
                      neoadj.tx = dataset$clinicalDatParsed$Neoadj.Tx,
                      neoadj.tx.clean = dataset$clinicalDatParsed$Neoadj.Regimen.clean,
                      M = dataset$clinicalDatParsed$M,
                      uniqID=dataset$sampInfo$uniqID,
                      time_diag = dataset$clinicalDatParsed$`Overall.Survival.(diagnosis.to.death.in.months)`,
                      event_recur = dataset$clinicalDatParsed$`Recurrence.Event.(0=NED.1=radiographic.recurrence,.2.=.documented.chemical.recurrence.alone,.500=died.of.operation,.600.=.died.of.documented.non-PDAC.event.with.NED.900=unable.to.determine.due.to.lack.of.reccords,.950=unable.to.determine.due.to.indeterminate.imaging.990.=.non-resected.PDAC.case,.999=non-PDAC.case)`,
                      whitelist = FALSE,
                      stringsAsFactors = FALSE)

survDat$event[survDat$event == 500 | 
                 survDat$event ==900 |
                 survDat$event ==600 |
                survDat$event ==650 ] <- 0
survDat$event[survDat$event == 2 | 
                 survDat$event ==3] <- 1
survDat$event[survDat$event_recur == 500 | 
                 survDat$event_recur ==900 |
                 survDat$event_recur ==600 |
                survDat$event_recur ==650 ] <- 0
survDat$event[survDat$event_recur == 2 | 
                 survDat$event_recur ==3] <- 1

survDat$event <- as.numeric(survDat$event)
survDat$time <- as.numeric(survDat$time)
survDat$time_diag <-as.numeric(survDat$time_diag)

# Merge pathCalls and Subtypes

dataset$pathCall$uniqID<-paste(dataset$pathCall$Library_ID,dataset$pathCall$Flowcell,sep = ":")

survDat_merged<-merge(survDat,data_sub,by="uniqID")

survDat_merged <- survDat_merged %>%
  left_join(dataset$subtypeCall %>% select(sampID,PurIST.prob,PurIST,PurIST.graded,DeCAF,DeCAF.prob,DeCAF.graded), by = "sampID") %>%
  left_join(dataset$pathCall %>% select(uniqID,`Collagenized(yes.1,.no.0)`,`Myxoid(yes.1,.no.0)`,`Myx1/mixed2/Coll3`), by = "uniqID")

survDat_merged <- survDat_merged %>% mutate_if(is.character,as.factor) %>%  mutate_at(c("Collagenized(yes.1,.no.0)","Myxoid(yes.1,.no.0)","Myx1/mixed2/Coll3") , as.factor)

survDat_merged$DeCAF.prob<-as.numeric(survDat_merged$DeCAF.prob)
survDat_merged$PurIST.prob <-as.numeric(survDat_merged$PurIST.prob)
survDat_merged$age <- as.numeric(survDat_merged$age)
survDat_merged$preop_ca199 <- as.numeric(survDat_merged$preop_ca199)
survDat_merged$Date.of.Dx <- as.numeric(survDat_merged$Date.of.Dx)
survDat_merged$Date.of.Surgery <- as.numeric(survDat_merged$Date.of.Surgery)
survDat_merged$Final.Date <- as.numeric(survDat_merged$Final.Date)
survDat_merged$Pos.LN <- as.numeric(survDat_merged$Pos.LN)
survDat_merged$T.LN <- as.numeric(survDat_merged$T.LN)
survDat_merged$pre_op_bmi <- as.numeric(survDat_merged$pre_op_bmi)

survDat <- survDat_merged


```

Define as.factor and as.numeric before using for cox-regression

```{r}

survDat <- survDat %>% 
  mutate_at(c("DeCAF.prob","PurIST.prob","age","pre_op_bmi", "preop_ca199", "Pos.LN","T.LN"), as.numeric) %>%
  mutate_at(c("neoadj.tx","DeCAF","DeCAF.graded","PurIST","PurIST.graded","Collagenized(yes.1,.no.0)","Myxoid(yes.1,.no.0)","Myx1/mixed2/Coll3","race", "sex", "tobacco_former_current_never", "alcohol_yn", "personal_hx_ca_yn", "bileduct_stent_clean", "preop_cholangitis_yn", "chronic_pancreatitis_yn", "Recent.ABX", "tumor_location.clean", "differentiation_clean_downstaged", "differentiation_clean_upstaged", "T.impute.from.TumorSize.8thEd", "N.impute.from.PosLN.8thEd", "Lymphovascular.Invasion.clean", "PNI.clean", "Margin.(close.<1mm)", "Stage.impute.TN.8thEd", "Neoadj.Regimen.clean", "neo_folfirinox.clean", "neo_GA", "neo_xrt.clean", "Path.Response.score.clean", "Adj.Tx.(Yes.if.got.any.treatment.for.PDAC).clean", "Adj_Tx.clean", "Recur.(NA.if.non-PDAC.or.non-resectable.disease,.even.if.treated.for.other.causes)"),as.factor)

```



## Cox-Regression and Survfit()

Cox-regression for numeric and categorical variables using coxph().

Pull p-value for each and store in a new dataframe. 

```{r cox}

p_df<-data.frame(variable=character(),p.value=numeric())

model_list<-list()
variable_list<- list()
survfit_list <- list()
survfit_list_cont <- list()

km <- with(survDat, Surv(time,event))

# 1. neoadj.tx ------------------------------------------------------------------

p1 = coxph(km ~ neoadj.tx, data = survDat)

# Extract variable and p-value from the Cox model
variable1 <- as.character(summary(p1)$call$formula[[3]])
p_value1 <- round(summary(p1)$logtest[[3]],4)
tmp.Dat1 <-data.frame(variable = variable1, p.value = p_value1)

variable_list[[variable1]]<-variable1
model_list [[variable1]] <-p1

p_df <- rbind(p_df,tmp.Dat1) 

km_fit1 <- survfit(km ~ neoadj.tx, data = survDat, type = "kaplan-meier")

survfit_list[[variable1]] <- km_fit1

# 2. DeCAF --------------------------------------------------------------------

p2 = coxph(km ~ DeCAF, data = survDat)

# Extract variable and p-value from the Cox model
variable2 <- as.character(summary(p2)$call$formula[[3]])
p_value2 <- round(summary(p2)$logtest[[3]],4)
tmp.Dat2 <-data.frame(variable = variable2, p.value = p_value2)

variable_list[[variable2]]<-variable2
model_list [[variable2]] <-p2

p_df <- rbind(p_df,tmp.Dat2) 

km_fit2 <- survfit(km ~ DeCAF, data = survDat, type = "kaplan-meier")

survfit_list[[variable2]] <- km_fit2

# 3. DeCAF.graded -----------------------------------------------------------------

p3 = coxph(km ~ DeCAF.graded, data = survDat)

# Extract variable and p-value from the Cox model
variable3 <- as.character(summary(p3)$call$formula[[3]])
p_value3 <- round(summary(p3)$logtest[[3]],4)
tmp.Dat3 <-data.frame(variable = variable3, p.value = p_value3)

variable_list[[variable3]]<-variable3
model_list [[variable3]] <-p3

p_df <- rbind(p_df,tmp.Dat3)

km_fit3 <- survfit(km ~ DeCAF.graded, data = survDat, type = "kaplan-meier")

survfit_list[[variable3]] <- km_fit3

# 4. DeCAF.prob --------------------------------------------------------------------

p4 = coxph(km ~ DeCAF.prob, data = survDat)

# Extract variable and p-value from the Cox model
variable4 <- as.character(summary(p4)$call$formula[[3]])
p_value4 <- round(summary(p4)$logtest[[3]],4)
tmp.Dat4 <-data.frame(variable = variable4, p.value = p_value4)

variable_list[[variable4]]<-variable4

model_list [[variable4]] <-p4

p_df <- rbind(p_df,tmp.Dat4)

km_fit4 <- survfit(km ~ DeCAF.prob, data = survDat, type = "kaplan-meier")

survfit_list_cont[[variable4]] <- km_fit4

# 5. PurIST --------------------------------------------------------------------

p5 = coxph(km ~ PurIST, data = survDat)

# Extract variable and p-value from the Cox model
variable5 <- as.character(summary(p5)$call$formula[[3]])
p_value5 <- round(summary(p5)$logtest[[3]],4)
tmp.Dat5 <-data.frame(variable = variable5, p.value = p_value5)

variable_list[[variable5]]<-variable5

model_list [[variable5]] <-p5
# Create a data frame
p_df <- rbind(p_df,tmp.Dat5) 

km_fit5 <- survfit(km ~ PurIST, data = survDat, type = "kaplan-meier")

survfit_list[[variable5]] <- km_fit5

# 6. PurIST.graded ----------------------------------------------------------------

p6 = coxph(km ~ PurIST.graded, data = survDat)

# Extract variable and p-value from the Cox model
variable6 <- as.character(summary(p6)$call$formula[[3]])
p_value6 <- round(summary(p6)$logtest[[3]],4)
tmp.Dat6 <-data.frame(variable = variable6, p.value = p_value6)

variable_list[[variable6]]<-variable6

model_list [[variable6]] <-p6
# Create a data frame
p_df <- rbind(p_df,tmp.Dat6)

km_fit6 <- survfit(km ~ PurIST.graded, data = survDat, type = "kaplan-meier")

survfit_list[[variable6]] <- km_fit6

# 7. PurIST.prob ------------------------------------------------------------------

p7 = coxph(km ~ PurIST.prob, data = survDat)

# Extract variable and p-value from the Cox model
variable7 <- as.character(summary(p7)$call$formula[[3]])
p_value7 <- round(summary(p7)$logtest[[3]],4)
tmp.Dat7 <-data.frame(variable = variable7, p.value = p_value7)
variable_list[[variable7]]<-variable7

model_list [[variable7]] <-p7
# Create a data frame
p_df <- rbind(p_df,tmp.Dat7)

km_fit7 <- survfit(km ~ PurIST.prob, data = survDat, type = "kaplan-meier")

survfit_list_cont[[variable7]] <- km_fit7

# 8. Collagenized(yes.1,.no.0) ----------------------------------------------------

p8 = coxph(km ~ `Collagenized(yes.1,.no.0)`, data = survDat)

# Extract variable and p-value from the Cox model
variable8 <- as.character(summary(p8)$call$formula[[3]])
p_value8 <- round(summary(p8)$logtest[[3]],4)
tmp.Dat8 <-data.frame(variable = variable8, p.value = p_value8)
variable_list[[variable8]]<-variable8

model_list [[variable8]] <-p8
# Create a data frame
p_df <- rbind(p_df,tmp.Dat8)

km_fit8 <- survfit(km ~ survDat$`Collagenized(yes.1,.no.0)`, data = survDat, type = "kaplan-meier")

survfit_list[[variable8]] <- km_fit8


# 9. Myxoid(yes.1,.no.0) ----------------------------------------------------------

p9 = coxph(km ~ `Myxoid(yes.1,.no.0)`, data = survDat)

# Extract variable and p-value from the Cox model
variable9 <- as.character(summary(p9)$call$formula[[3]])
p_value9 <- round(summary(p9)$logtest[[3]],4)
tmp.Dat9 <-data.frame(variable = variable9, p.value = p_value9)
variable_list[[variable9]]<-variable9

model_list [[variable9]] <-p9
# Create a data frame
p_df <- rbind(p_df,tmp.Dat9)

km_fit9 <- survfit(km ~ survDat$`Myxoid(yes.1,.no.0)`, data = survDat, type = "kaplan-meier")

survfit_list[[variable9]] <- km_fit9


# 10. Myx1/mixed2/Coll3 ------------------------------------------------------------

p10 = coxph(km ~ `Myx1/mixed2/Coll3`, data = survDat)

# Extract variable and p-value from the Cox model
variable10 <- as.character(summary(p10)$call$formula[[3]])
p_value10 <- round(summary(p10)$logtest[[3]],4)
tmp.Dat10 <-data.frame(variable = variable10, p.value = p_value10)
model_list [[variable10]] <-p10
variable_list[[variable10]]<-variable10

# Create a data frame
p_df <- rbind(p_df,tmp.Dat10)

km_fit10 <- survfit(km ~ survDat$`Myx1/mixed2/Coll3`, data = survDat, type = "kaplan-meier")

survfit_list[[variable10]] <- km_fit10


# 11. age --------------------------------------------------------------------

p11 = coxph(km ~ age, data = survDat)

# Extract variable and p-value from the Cox model
variable11 <- as.character(summary(p11)$call$formula[[3]])
p_value11 <- round(summary(p11)$logtest[[3]],4)
tmp.Dat11 <-data.frame(variable = variable11, p.value = p_value11)
variable_list[[variable11]]<-variable11

model_list [[variable11]] <-p11
# Create a data frame
p_df <- rbind(p_df,tmp.Dat11)

km_fit11 <- survfit(km ~ age, data = survDat, type = "kaplan-meier")

survfit_list_cont[[variable11]] <- km_fit11

# 12. race --------------------------------------------------------------------

p12 = coxph(km ~ race, data = survDat)

# Extract variable and p-value from the Cox model
variable12 <- as.character(summary(p12)$call$formula[[3]])
p_value12 <- round(summary(p12)$logtest[[3]],4)
tmp.Dat12 <-data.frame(variable = variable12, p.value = p_value12)
model_list [[variable12]] <-p12
variable_list[[variable12]]<-variable12

# Create a data frame
p_df <- rbind(p_df,tmp.Dat12) 

km_fit12 <- survfit(km ~ race, data = survDat, type = "kaplan-meier")

survfit_list[[variable12]] <- km_fit12

# 13. sex --------------------------------------------------------------------

p13 = coxph(km ~ sex, data = survDat)

# Extract variable and p-value from the Cox model
variable13 <- as.character(summary(p13)$call$formula[[3]])
p_value13 <- round(summary(p13)$logtest[[3]],4)
tmp.Dat13<-data.frame(variable = variable13, p.value = p_value13)
variable_list[[variable13]]<-variable13

model_list [[variable13]] <-p13
# Create a data frame
p_df <- rbind(p_df,tmp.Dat13) 

km_fit13 <- survfit(km ~ sex, data = survDat, type = "kaplan-meier")

survfit_list[[variable13]] <- km_fit13

# 46. pre_op_bmi --------------------------------------------------------------------

p46 = coxph(km ~ pre_op_bmi, data = survDat)

# Extract variable and p-value from the Cox model
variable46 <- as.character(summary(p46)$call$formula[[3]])
p_value46 <- round(summary(p46)$logtest[[3]],4)
tmp.Dat46<-data.frame(variable = variable46, p.value = p_value46)
variable_list[[variable46]]<-variable46

model_list [[variable46]] <-p46
# Create a data frame
p_df <- rbind(p_df,tmp.Dat46)

km_fit46 <- survfit(km ~ pre_op_bmi, data = survDat, type = "kaplan-meier")

survfit_list_cont[[variable46]] <- km_fit46

# 14. tobacco_former_current_never --------------------------------------------------------------------

p14 = coxph(km ~ tobacco_former_current_never, data = survDat)

# Extract variable and p-value from the Cox model
variable14 <- as.character(summary(p14)$call$formula[[3]])
p_value14 <- round(summary(p14)$logtest[[3]],4)
tmp.Dat14 <-data.frame(variable = variable14, p.value = p_value14)
variable_list[[variable14]]<-variable14

model_list [[variable14]] <-p14
# Create a data frame
p_df <- rbind(p_df,tmp.Dat14) 

km_fit14 <- survfit(km ~ tobacco_former_current_never, data = survDat, type = "kaplan-meier")

survfit_list[[variable14]] <- km_fit14

# 15. alcohol_yn --------------------------------------------------------------------

p15 = coxph(km ~ alcohol_yn, data = survDat)

# Extract variable and p-value from the Cox model
variable15 <- as.character(summary(p15)$call$formula[[3]])
p_value15 <- round(summary(p15)$logtest[[3]],4)
tmp.Dat15<-data.frame(variable = variable15, p.value = p_value15)
variable_list[[variable15]]<-variable15

model_list [[variable15]] <-p15
# Create a data frame
p_df <- rbind(p_df,tmp.Dat15) 

km_fit15 <- survfit(km ~ alcohol_yn, data = survDat, type = "kaplan-meier")

survfit_list[[variable15]] <- km_fit15

# 16. personal_hx_ca_yn -------------------------------------------------

p16 = coxph(km ~ personal_hx_ca_yn, data = survDat)

# Extract variable and p-value from the Cox model
variable16 <- as.character(summary(p16)$call$formula[[3]])
p_value16 <- round(summary(p16)$logtest[[3]],4)
tmp.Dat16 <-data.frame(variable = variable16, p.value = p_value16)
variable_list[[variable16]]<-variable16

model_list [[variable16]] <-p16
# Create a data frame
p_df <- rbind(p_df,tmp.Dat16) 

km_fit16 <- survfit(km ~ personal_hx_ca_yn, data = survDat, type = "kaplan-meier")

survfit_list[[variable16]] <- km_fit16

# 17. bileduct_stent_clean ---------------------------------------------------------

p17 = coxph(km ~ bileduct_stent_clean, data = survDat)

# Extract variable and p-value from the Cox model
variable17 <- as.character(summary(p17)$call$formula[[3]])
p_value17 <- round(summary(p17)$logtest[[3]],4)
tmp.Dat17<-data.frame(variable = variable17, p.value = p_value17)
variable_list[[variable17]]<-variable17

model_list [[variable17]] <-p17
# Create a data frame
p_df <- rbind(p_df,tmp.Dat17) 

km_fit17 <- survfit(km ~ bileduct_stent_clean, data = survDat, type = "kaplan-meier")

survfit_list[[variable17]] <- km_fit17


# 18. preop_ca199 -------------------------------------------------------------------

p18 = coxph(km ~ preop_ca199, data = survDat)

# Extract variable and p-value from the Cox model
variable18 <- as.character(summary(p18)$call$formula[[3]])
p_value18 <- round(summary(p18)$logtest[[3]],4)
tmp.Dat18<-data.frame(variable = variable18, p.value = p_value18)
variable_list[[variable18]]<-variable18

model_list [[variable18]] <-p18
# Create a data frame
p_df <- rbind(p_df,tmp.Dat18)

km_fit18 <- survfit(km ~ preop_ca199, data = survDat, type = "kaplan-meier")

survfit_list_cont[[variable18]] <- km_fit18

# 19. preop_cholangitis_yn ---------------------------------------------------------

p19 = coxph(km ~ preop_cholangitis_yn, data = survDat)

# Extract variable and p-value from the Cox model
variable19 <- as.character(summary(p19)$call$formula[[3]])
p_value19 <- round(summary(p19)$logtest[[3]],4)
tmp.Dat19<-data.frame(variable = variable19, p.value = p_value19)
variable_list[[variable19]]<-variable19

model_list [[variable19]] <-p19
# Create a data frame
p_df <- rbind(p_df,tmp.Dat19) 

km_fit19 <- survfit(km ~ preop_cholangitis_yn, data = survDat, type = "kaplan-meier")

survfit_list[[variable19]] <- km_fit19


# 20. chronic_pancreatitis_yn ---------------------------------------------------------

p20 = coxph(km ~ chronic_pancreatitis_yn, data = survDat)

# Extract variable and p-value from the Cox model
variable20 <- as.character(summary(p20)$call$formula[[3]])
p_value20 <- round(summary(p20)$logtest[[3]],4)
tmp.Dat20<-data.frame(variable = variable20, p.value = p_value20)
variable_list[[variable20]]<-variable20

model_list [[variable20]] <-p20
# Create a data frame
p_df <- rbind(p_df,tmp.Dat20) 

km_fit20 <- survfit(km ~ chronic_pancreatitis_yn, data = survDat, type = "kaplan-meier")

survfit_list[[variable20]] <- km_fit20


# 21. Recent ABX ---------------------------------------------------------

p21 = coxph(km ~ Recent.ABX, data = survDat)

# Extract variable and p-value from the Cox model
variable21 <- as.character(summary(p21)$call$formula[[3]])
p_value21 <- round(summary(p21)$logtest[[3]],4)
tmp.Dat21<-data.frame(variable = variable21, p.value = p_value21)
variable_list[[variable21]]<-variable21

model_list [[variable21]] <-p21
# Create a data frame
p_df <- rbind(p_df,tmp.Dat21) 

km_fit21 <- survfit(km ~ Recent.ABX, data = survDat, type = "kaplan-meier")

survfit_list[[variable21]] <- km_fit21

# 22. Tumor Location (Binary) ---------------------------------------------------------

p22 = coxph(km ~ tumor_location.clean, data = survDat)

# Extract variable and p-value from the Cox model
variable22 <- as.character(summary(p22)$call$formula[[3]])
p_value22 <- round(summary(p22)$logtest[[3]],4)
tmp.Dat22<-data.frame(variable = variable22, p.value = p_value22)
variable_list[[variable22]]<-variable22

model_list [[variable22]] <-p22
# Create a data frame
p_df <- rbind(p_df,tmp.Dat22)

km_fit22 <- survfit(km ~ tumor_location.clean, data = survDat, type = "kaplan-meier")

survfit_list[[variable22]] <- km_fit22

# 23. Date.of.Surgery ---------------------------------------------------------

p23 = coxph(km ~ Date.of.Surgery, data = survDat)

# Extract variable and p-value from the Cox model
variable23 <- as.character(summary(p23)$call$formula[[3]])
p_value23 <- round(summary(p23)$logtest[[3]],4)
tmp.Dat23<-data.frame(variable = variable23, p.value = p_value23)
variable_list[[variable23]]<-variable23

model_list [[variable23]] <-p23
# Create a data frame
p_df <- rbind(p_df,tmp.Dat23) 

km_fit23 <- survfit(km ~ Date.of.Surgery, data = survDat, type = "kaplan-meier")

survfit_list_cont[[variable23]] <- km_fit23

# 24. Date.of.Dx ---------------------------------------------------------

p24 = coxph(km ~ Date.of.Dx, data = survDat)

# Extract variable and p-value from the Cox model
variable24 <- as.character(summary(p24)$call$formula[[3]])
p_value24 <- round(summary(p24)$logtest[[3]],4)
tmp.Dat24<-data.frame(variable = variable24, p.value = p_value24)
variable_list[[variable24]]<-variable24

model_list [[variable24]] <-p24
# Create a data frame
p_df <- rbind(p_df,tmp.Dat24)

km_fit24 <- survfit(km ~ Date.of.Dx, data = survDat, type = "kaplan-meier")

survfit_list_cont[[variable24]] <- km_fit24

# 25. Final.Date ---------------------------------------------------------

p25 = coxph(km ~ Final.Date, data = survDat)

# Extract variable and p-value from the Cox model
variable25 <- as.character(summary(p25)$call$formula[[3]])
p_value25 <- round(summary(p25)$logtest[[3]],4)
tmp.Dat25<-data.frame(variable = variable25, p.value = p_value25)
variable_list[[variable25]]<-variable25

model_list [[variable25]] <-p25
# Create a data frame
p_df <- rbind(p_df,tmp.Dat25)

km_fit25 <- survfit(km ~ Final.Date, data = survDat, type = "kaplan-meier")

survfit_list_cont[[variable25]] <- km_fit25


# 26. Recurrence.Event ---------------------------------------------------------

# p26 = coxph(km ~ event_recur), data = survDat)
# 
# # Extract variable and p-value from the Cox model
# variable26 <- as.character(summary(p26)$call$formula[[3]])
# p_value26 <- round(summary(p26)$logtest[[3]],4)
# tmp.Dat26<-data.frame(variable = variable26, p.value = p_value26)
# variable_list[[variable26]]<-variable26
# 
# model_list [[variable26]] <-p26
# # Create a data frame
# p_df <- rbind(p_df,tmp.Dat26)
# 
# km_fit26 <- survfit(km ~ event_recur, data = survDat, type = "kaplan-meier")

#survfit_list[[variable26]] <- km_fit26

# 27. differentiation_clean_upstaged ---------------------------------------------------------

p27 = coxph(km ~ differentiation_clean_upstaged, data = survDat)

# Extract variable and p-value from the Cox model
variable27 <- as.character(summary(p27)$call$formula[[3]])
p_value27 <- round(summary(p27)$logtest[[3]],4)
tmp.Dat27<-data.frame(variable = variable27, p.value = p_value27)
variable_list[[variable27]]<-variable27

model_list [[variable27]] <-p27
# Create a data frame
p_df <- rbind(p_df,tmp.Dat27) 

km_fit27 <- survfit(km ~ differentiation_clean_upstaged, data = survDat, type = "kaplan-meier")

survfit_list[[variable27]] <- km_fit27

# 28. differentiation_clean_downstaged ---------------------------------------------------------

p28 = coxph(km ~ differentiation_clean_downstaged, data = survDat)

# Extract variable and p-value from the Cox model
variable28 <- as.character(summary(p28)$call$formula[[3]])
p_value28 <- round(summary(p28)$logtest[[3]],4)
tmp.Dat28<-data.frame(variable = variable28, p.value = p_value28)
variable_list[[variable28]]<-variable28

model_list [[variable28]] <-p28
# Create a data frame
p_df <- rbind(p_df,tmp.Dat28) 

km_fit28 <- survfit(km ~ differentiation_clean_downstaged, data = survDat, type = "kaplan-meier")

survfit_list[[variable28]] <- km_fit28

# # 29a. T.original.clean -----------------------------------------------------------------------
# 
# p29a = coxph(km ~ T.original.clean), data = survDat)
# 
# # Extract variable and p-value from the Cox model
# variable29a <- as.character(summary(p29a)$call$formula[[3]])
# p_value29a <- round(summary(p29a)$logtest[[3]],4)
# tmp.Dat29a<-data.frame(variable = variable29a, p.value = p_value29a)
# variable_list[[variable29a]]<-variable29a
# 
# model_list [[variable29a]] <-p29a
# # Create a data frame
# p_df <- rbind(p_df,tmp.Dat29a) 
# 
# km_fit29a <- survfit(km ~ T.original.clean, data = survDat, type = "kaplan-meier")
# 
# survfit_list[[variable29a]] <- km_fit29a

# 29. T.impute --------------------------------------------------------------------

p29 = coxph(km ~ T.impute.from.TumorSize.8thEd, data = survDat)

# Extract variable and p-value from the Cox model
variable29 <- as.character(summary(p29)$call$formula[[3]])
p_value29 <- round(summary(p29)$logtest[[3]],4)
tmp.Dat29<-data.frame(variable = variable29, p.value = p_value29)
variable_list[[variable29]]<-variable29

model_list [[variable29]] <-p29
# Create a data frame
p_df <- rbind(p_df,tmp.Dat29) 

km_fit29 <- survfit(km ~ T.impute.from.TumorSize.8thEd, data = survDat, type = "kaplan-meier")

survfit_list[[variable29]] <- km_fit29

# # 30a. N -------------------------------------------------------------------
# 
# p30a = coxph(km ~ N), data = survDat)
# 
# # Extract variable and p-value from the Cox model
# variable30a <- as.character(summary(p30a)$call$formula[[3]])
# p_value30a <- round(summary(p30a)$logtest[[3]],4)
# tmp.Dat30a<-data.frame(variable = variable30a, p.value = p_value30a)
# variable_list[[variable30a]]<-variable30a
# 
# model_list [[variable30a]] <-p30a
# # Create a data frame
# p_df <- rbind(p_df,tmp.Dat30a) 
# 
# km_fit30a <- survfit(km ~ N, data = survDat, type = "kaplan-meier")
# 
# survfit_list[[variable30a]] <- km_fit30a

# 30. N.impute -------------------------------------------------------------------

p30 = coxph(km ~ N.impute.from.PosLN.8thEd, data = survDat)

# Extract variable and p-value from the Cox model
variable30 <- as.character(summary(p30)$call$formula[[3]])
p_value30 <- round(summary(p30)$logtest[[3]],4)
tmp.Dat30<-data.frame(variable = variable30, p.value = p_value30)
variable_list[[variable30]]<-variable30

model_list [[variable30]] <-p30
# Create a data frame
p_df <- rbind(p_df,tmp.Dat30) 

km_fit30 <- survfit(km ~ N.impute.from.PosLN.8thEd, data = survDat, type = "kaplan-meier")

survfit_list[[variable30]] <- km_fit30

# 31. M -------------------------------------------------------------------

# p = coxph(km ~ M), data = survDat)
# 
# # Extract variable and p-value from the Cox model
# variable <- as.character(summary(p)$call$formula[[3]])
# p_value31 <- round(summary(p)$logtest[[3]],4)
# tmp.Dat31<-data.frame(variable = variable, p.value = p_value31)
# variable_list[[variable]]<-variable
# 
# model_list [[variable]] <-p
# # Create a data frame
# p_df <- rbind(p_df,tmp.Dat31) 

km_fit31 <- survfit(km ~ M, data = survDat, type = "kaplan-meier")

survfit_list[["M"]] <- km_fit31

# 32. Pos.LN --------------------------------------------------------------------

p32 = coxph(km ~ Pos.LN, data = survDat)

# Extract variable and p-value from the Cox model
variable32 <- as.character(summary(p32)$call$formula[[3]])
p_value32 <- round(summary(p32)$logtest[[3]],4)
tmp.Dat32<-data.frame(variable = variable32, p.value = p_value32)
variable_list[[variable32]]<-variable32

model_list [[variable32]] <-p32
# Create a data frame
p_df <- rbind(p_df,tmp.Dat32)

km_fit32 <- survfit(km ~ Pos.LN, data = survDat, type = "kaplan-meier")

survfit_list_cont[[variable32]] <- km_fit32

# 33. T.LN --------------------------------------------------------------------

p33 = coxph(km ~ T.LN, data = survDat)

# Extract variable and p-value from the Cox model
variable33 <- as.character(summary(p33)$call$formula[[3]])
p_value33 <- round(summary(p33)$logtest[[3]],4)
tmp.Dat33<-data.frame(variable = variable33, p.value = p_value33)
variable_list[[variable33]]<-variable33

model_list [[variable33]] <-p33
# Create a data frame
p_df <- rbind(p_df,tmp.Dat33)

km_fit33 <- survfit(km ~ T.LN, data = survDat, type = "kaplan-meier")

survfit_list_cont[[variable33]] <- km_fit33

# 34. Lymphovascular.Invasion.clean ------------------------------------------------------

p34 = coxph(km ~ Lymphovascular.Invasion.clean, data = survDat)

# Extract variable and p-value from the Cox model
variable34 <- as.character(summary(p34)$call$formula[[3]])
p_value34 <- round(summary(p34)$logtest[[3]],4)
tmp.Dat34<-data.frame(variable = variable34, p.value = p_value34)
variable_list[[variable34]]<-variable34

model_list [[variable34]] <-p34
# Create a data frame
p_df <- rbind(p_df,tmp.Dat34) 

km_fit34 <- survfit(km ~ Lymphovascular.Invasion.clean, data = survDat, type = "kaplan-meier")

survfit_list[[variable34]] <- km_fit34

# 35. PNI.clean ------------------------------------------------------------------

p35 = coxph(km ~ PNI.clean, data = survDat)

# Extract variable and p-value from the Cox model
variable35 <- as.character(summary(p35)$call$formula[[3]])
p_value35 <- round(summary(p35)$logtest[[3]],4)
tmp.Dat35<-data.frame(variable = variable35, p.value = p_value35)
variable_list[[variable35]]<-variable35

model_list [[variable35]] <-p35
# Create a data frame
p_df <- rbind(p_df,tmp.Dat35)

km_fit35 <- survfit(km ~ PNI.clean, data = survDat, type = "kaplan-meier")

survfit_list[[variable35]] <- km_fit35

# 36. Margin.(close.<1mm) ----------------------------------------------------------

p36 = coxph(km ~ `Margin.(close.<1mm)`, data = survDat)

# Extract variable and p-value from the Cox model
variable36 <- as.character(summary(p36)$call$formula[[3]])
p_value36 <- round(summary(p36)$logtest[[3]],4)
tmp.Dat36<-data.frame(variable = variable36, p.value = p_value36)
variable_list[[variable36]]<-variable36

model_list [[variable36]] <-p36
# Create a data frame
p_df <- rbind(p_df,tmp.Dat36)

km_fit36 <- survfit(km ~ survDat$`Margin.(close.<1mm)`, data = survDat, type = "kaplan-meier")

survfit_list[[variable36]] <- km_fit36


# 37a. Stage.impute --------------------------------------------------------------------
# 
# p37a = coxph(km ~ Stage.original.clean), data = survDat)
# 
# # Extract variable and p-value from the Cox model
# variable37a <- as.character(summary(p37a)$call$formula[[3]])
# p_value37a <- round(summary(p37a)$logtest[[3]],4)
# tmp.Dat37a<-data.frame(variable = variable37a, p.value = p_value37a)
# variable_list[[variable37a]]<-variable37a
# 
# model_list [[variable37a]] <-p37a
# # Create a data frame
# p_df <- rbind(p_df,tmp.Dat37a)
# 
# km_fit37a <- survfit(km ~ Stage.original.clean, data = survDat, type = "kaplan-meier")
# 
# survfit_list[[variable37a]] <- km_fit37a

# 37. Stage.impute.8thEd --------------------------------------------------------------------

p37 = coxph(km ~ Stage.impute.TN.8thEd, data = survDat)

# Extract variable and p-value from the Cox model
variable37 <- as.character(summary(p37)$call$formula[[3]])
p_value37 <- round(summary(p37)$logtest[[3]],4)
tmp.Dat37<-data.frame(variable = variable37, p.value = p_value37)
variable_list[[variable37]]<-variable37

model_list [[variable37]] <-p37
# Create a data frame
p_df <- rbind(p_df,tmp.Dat37)

km_fit37 <- survfit(km ~ Stage.impute.TN.8thEd, data = survDat, type = "kaplan-meier")

survfit_list[[variable37]] <- km_fit37

# 38. Neoadj.Regimen.clean ---------------------------------------------------------------

p38 = coxph(km ~ Neoadj.Regimen.clean, data = survDat)

# Extract variable and p-value from the Cox model
variable38 <- as.character(summary(p38)$call$formula[[3]])
p_value38 <- round(summary(p38)$logtest[[3]],4)
tmp.Dat38<-data.frame(variable = variable38, p.value = p_value38)
variable_list[[variable38]]<-variable38

model_list [[variable38]] <-p38
# Create a data frame
p_df <- rbind(p_df,tmp.Dat38)

km_fit38 <- survfit(km ~ Neoadj.Regimen.clean, data = survDat, type = "kaplan-meier")

survfit_list[[variable38]] <- km_fit38

# 39. neo_folfirinox.clean ---------------------------------------------------------------

p39 = coxph(km ~ neo_folfirinox.clean, data = survDat)

# Extract variable and p-value from the Cox model
variable39 <- as.character(summary(p39)$call$formula[[3]])
p_value39 <- round(summary(p39)$logtest[[3]],4)
tmp.Dat39<-data.frame(variable = variable39, p.value = p_value39)
variable_list[[variable39]]<-variable39

model_list [[variable39]] <-p39
# Create a data frame
p_df <- rbind(p_df,tmp.Dat39)

km_fit39 <- survfit(km ~ neo_folfirinox.clean, data = survDat, type = "kaplan-meier")

survfit_list[[variable39]] <- km_fit39


# 40. neo_GA --------------------------------------------------------------------

p40 = coxph(km ~ neo_GA, data = survDat)

# Extract variable and p-value from the Cox model
variable40 <- as.character(summary(p40)$call$formula[[3]])
p_value40 <- round(summary(p40)$logtest[[3]],4)
tmp.Dat40<-data.frame(variable = variable40, p.value = p_value40)
variable_list[[variable40]]<-variable40

model_list [[variable40]] <-p40

# Create a data frame
p_df <- rbind(p_df,tmp.Dat40)

km_fit40 <- survfit(km ~ neo_GA, data = survDat, type = "kaplan-meier")

survfit_list[[variable40]] <- km_fit40

# 41. neo_xrt.clean --------------------------------------------------------------------

p41 = coxph(km ~ neo_xrt.clean, data = survDat)

# Extract variable and p-value from the Cox model
variable41 <- as.character(summary(p41)$call$formula[[3]])
p_value41 <- round(summary(p41)$logtest[[3]],4)
tmp.Dat41<-data.frame(variable = variable41, p.value = p_value41)
variable_list[[variable41]]<-variable41

model_list [[variable41]] <-p41
# Create a data frame
p_df <- rbind(p_df,tmp.Dat41)

km_fit41 <- survfit(km ~ neo_xrt.clean, data = survDat, type = "kaplan-meier")

survfit_list[[variable41]] <- km_fit41

# 42. Path.Response.score.clean -----------------------------------------------------

p42 = coxph(km ~ Path.Response.score.clean, data = survDat)

# Extract variable and p-value from the Cox model
variable42 <- as.character(summary(p42)$call$formula[[3]])
p_value42 <- round(summary(p42)$logtest[[3]],4)
tmp.Dat42<-data.frame(variable = variable42, p.value = p_value42)
variable_list[[variable42]]<-variable42

model_list [[variable42]] <-p42
# Create a data frame
p_df <- rbind(p_df,tmp.Dat42)

km_fit42 <- survfit(km ~ Path.Response.score.clean, data = survDat, type = "kaplan-meier")

survfit_list[[variable42]] <- km_fit42


# 43. "Adj.Tx.(Yes.if.got.any.treatment.for.PDAC).clean"-----------------------------------
p43 = coxph(km ~ `Adj.Tx.(Yes.if.got.any.treatment.for.PDAC).clean`, data = survDat)

# Extract variable and p-value from the Cox model
variable43 <- as.character(summary(p43)$call$formula[[3]])
p_value43 <- round(summary(p43)$logtest[[3]],4)
tmp.Dat43<-data.frame(variable = variable43, p.value = p_value43)
variable_list[[variable43]]<-variable43

model_list [[variable43]] <-p43
# Create a data frame
p_df <- rbind(p_df,tmp.Dat43) 

km_fit43 <- survfit(km ~ survDat$`Adj.Tx.(Yes.if.got.any.treatment.for.PDAC).clean`, data = survDat, type = "kaplan-meier")

survfit_list[[variable43]] <- km_fit43

# 44. "Adj_Tx.clean" ---------------------------------------------------------------------

p44 = coxph(km ~ Adj_Tx.clean, data = survDat)

# Extract variable and p-value from the Cox model
variable44 <- as.character(summary(p44)$call$formula[[3]])
p_value44 <- round(summary(p44)$logtest[[3]],4)
tmp.Dat44<-data.frame(variable = variable44, p.value = p_value44)
variable_list[[variable44]]<-variable44

model_list [[variable44]] <-p44

# Create a data frame
p_df <- rbind(p_df,tmp.Dat44) 

km_fit44 <- survfit(km ~ Adj_Tx.clean, data = survDat, type = "kaplan-meier")

survfit_list[[variable44]] <- km_fit44

#45. "Recur.(NA.if.non-PDAC.or.non-resectable.disease,.even.if.treated.for.other.causes)"------------------------------------------------------

p45 = coxph(km ~ `Recur.(NA.if.non-PDAC.or.non-resectable.disease,.even.if.treated.for.other.causes)`, data = survDat)

# Extract variable and p-value from the Cox model
variable45 <- as.character(summary(p45)$call$formula[[3]])
p_value45 <- round(summary(p45)$logtest[[3]],4)
tmp.Dat45<-data.frame(variable = variable45, p.value = p_value45)
variable_list[[variable45]]<-variable45

model_list [[variable45]] <-p45
# Create a data frame
p_df <- rbind(p_df,tmp.Dat45) 

km_fit45 <- survfit(km ~ survDat$`Recur.(NA.if.non-PDAC.or.non-resectable.disease,.even.if.treated.for.other.causes)`, data = survDat, type = "kaplan-meier")

survfit_list[[variable45]] <- km_fit45


```

### Write to excel

```{r excel}

#save as excel

write.xlsx(p_df,file = "/work/users/a/r/arthih/Laura_Clinical_Parsing/Survival_pValues_121323.xlsx")

```

```{r tbl}

tbl_list<-list()

for (i in seq_along(model_list)){
  tbl <- model_list[[i]] %>% tbl_regression()
  tbl_list [[i]] <-tbl
}

tbl_exp_list<-list()

for (i in seq_along(model_list)){
  tbl <- model_list[[i]] %>% tbl_regression(exponentiate = T)
  tbl_exp_list [[i]] <-tbl
}

tbl<-tbl_stack(tbl_list)
tbl_exp<-tbl_stack(tbl_exp_list)

tbl_exp_df <- tbl_exp %>% bold_labels() %>% as.data.frame()

merged_tbl<-tbl_merge(list(tbl, tbl_exp)) %>% bold_labels()

merged_tbl %>% as_gt() %>% gt::gtsave("Coxph_HR_Exp_121323.html")

tbl_df<-merged_tbl %>% as.data.frame()
tbl_df<-tbl_df[,-4]
colnames(tbl_df)<-c("Variables","log(HR)","95%CI","exp(HR)","exp(95%CI)","p-value")

```

### GT table for Categorical variables

Publication ready table

```{r tbl2}

surv_tbl_time <- survfit_list %>% tbl_survfit(times = c(6,12,24,60),
                                              label_header = "**{time} Months**"
                                               ) %>% add_p(test = "logrank")

surv_tbl_median <- survfit_list %>% tbl_survfit(probs = 0.5,
                                                label_header = "**Median (95% CI)**"
                                                ) %>% add_n() %>% add_nevent()

surv_tbl_cat <- tbl_merge(list(surv_tbl_median,surv_tbl_time), tab_spanner = F)

# surv_tbl_cat %>% bold_labels() %>% as_gt %>% gt::gtsave("/work/users/a/r/arthih/Laura_Clinical_Parsing/Survival_fit_Categorical_variables_112623.html")
```
### merge tables


```{r merge}

tbl_merge(list(tbl_n,tbl_nevent,surv_tbl_cat, tbl_exp)
) %>% as_gt %>% gt::gtsave("Univariate_Survival.html")
#gtsummary::as_flex_table() %>%
 # flextable::set_caption("Hzard ratios from Cox PH model and Survival times from Survfit")


```

## Add N 
25th April 2024.

```{r}
# calculate the total N by variable
tbl_n <- survDat %>%select( neoadj.tx,
                            DeCAF,
                            DeCAF.graded,
                            PurIST,
                            PurIST.graded,
                            `Collagenized(yes.1,.no.0)`,
                            `Myxoid(yes.1,.no.0)`,
                            `Myx1/mixed2/Coll3`,
                            race,
                            sex,
                            tobacco_former_current_never,
                            alcohol_yn,
                            personal_hx_ca_yn,
                            bileduct_stent_clean,
                            preop_cholangitis_yn,
                            chronic_pancreatitis_yn,
                            Recent.ABX,
                            tumor_location.clean,
                            event_recur,
                            differentiation_clean_upstaged,
                            differentiation_clean_downstaged,
                            T.impute.from.TumorSize.8thEd,
                            N.impute.from.PosLN.8thEd,
                            M,
                            Lymphovascular.Invasion.clean,
                            PNI.clean,
                            `Margin.(close.<1mm)`,
                            Stage.impute.TN.8thEd,
                            Neoadj.Regimen.clean,
                            neo_folfirinox.clean,
                            neo_GA,
                            neo_xrt.clean,
                            Path.Response.score.clean,
                            `Adj.Tx.(Yes.if.got.any.treatment.for.PDAC).clean`,
                            Adj_Tx.clean,
                            `Recur.(NA.if.non-PDAC.or.non-resectable.disease,.even.if.treated.for.other.causes)`,
                            DeCAF.prob,
                            PurIST.prob,
                            age,
                            pre_op_bmi,
                            preop_ca199,
                            Date.of.Surgery,
                            Date.of.Dx,
                            Final.Date,
                            Pos.LN,
                            T.LN) %>%
  tbl_summary(statistic = all_categorical() ~ "{n}", type = list(c(neoadj.tx,alcohol_yn,bileduct_stent_clean, personal_hx_ca_yn, preop_cholangitis_yn,chronic_pancreatitis_yn,Recent.ABX,Lymphovascular.Invasion.clean,PNI.clean,neo_folfirinox.clean,neo_GA,neo_xrt.clean,`Adj.Tx.(Yes.if.got.any.treatment.for.PDAC).clean`,Adj_Tx.clean,`Recur.(NA.if.non-PDAC.or.non-resectable.disease,.even.if.treated.for.other.causes)`)~'categorical'),missing = "no") %>%
  modify_header(stat_0 ~ "**N**") %>% add_n() %>%
  modify_footnote(everything() ~ NA)  

# calculate the event N by variable
tbl_nevent <- survDat %>% filter(event == 2) %>% select( neoadj.tx,
                            DeCAF,
                            DeCAF.graded,
                            PurIST,
                            PurIST.graded,
                            `Collagenized(yes.1,.no.0)`,
                            `Myxoid(yes.1,.no.0)`,
                            `Myx1/mixed2/Coll3`,
                            race,
                            sex,
                            tobacco_former_current_never,
                            alcohol_yn,
                            personal_hx_ca_yn,
                            bileduct_stent_clean,
                            preop_cholangitis_yn,
                            chronic_pancreatitis_yn,
                            Recent.ABX,
                            tumor_location.clean,
                            event_recur,
                            differentiation_clean_upstaged,
                            differentiation_clean_downstaged,
                            T.impute.from.TumorSize.8thEd,
                            N.impute.from.PosLN.8thEd,
                            M,
                            Lymphovascular.Invasion.clean,
                            PNI.clean,
                            `Margin.(close.<1mm)`,
                            Stage.impute.TN.8thEd,
                            Neoadj.Regimen.clean,
                            neo_folfirinox.clean,
                            neo_GA,
                            neo_xrt.clean,
                            Path.Response.score.clean,
                            `Adj.Tx.(Yes.if.got.any.treatment.for.PDAC).clean`,
                            Adj_Tx.clean,
                            `Recur.(NA.if.non-PDAC.or.non-resectable.disease,.even.if.treated.for.other.causes)`,DeCAF.prob,PurIST.prob,age,pre_op_bmi,preop_ca199,Date.of.Surgery,Date.of.Dx,Final.Date,Pos.LN,T.LN) %>% 
  tbl_summary(statistic = all_categorical() ~ "{n}", type = list(c(neoadj.tx,personal_hx_ca_yn, preop_cholangitis_yn,chronic_pancreatitis_yn,Recent.ABX,alcohol_yn,bileduct_stent_clean,Lymphovascular.Invasion.clean,PNI.clean,neo_folfirinox.clean,neo_GA,neo_xrt.clean,`Adj.Tx.(Yes.if.got.any.treatment.for.PDAC).clean`,Adj_Tx.clean,`Recur.(NA.if.non-PDAC.or.non-resectable.disease,.even.if.treated.for.other.causes)`)~'categorical'),missing = "no") %>%
  modify_header(stat_0 ~ "**Event N**")  %>% add_n() %>%
  modify_footnote(everything() ~ NA)


tbl_merge(list(tbl_n,tbl_nevent)) %>% as_gt() %>% gt::gtsave("N_variables_042524.html")
```



```{r tbl_style, eval=FALSE}
surv_tbl_cat[["table_body"]][["label"]][23]
surv_tbl_cat[["table_body"]][["label"]][26]
surv_tbl_cat[["table_body"]][["label"]][29]
surv_tbl_cat[["table_body"]][["label"]][97]
surv_tbl_cat[["table_body"]][["label"]][124]
surv_tbl_cat[["table_body"]][["label"]][130]
surv_tbl_cat[["table_body"]][["label"]][23]<-"Collagenized(yes.1,.no.0)"
surv_tbl_cat[["table_body"]][["label"]][26]<-"Myxoid(yes.1,.no.0)"
surv_tbl_cat[["table_body"]][["label"]][29]<-"Myx1/mixed2/Coll3"
surv_tbl_cat[["table_body"]][["label"]][97]<- "Margin.(close.<1mm)"
surv_tbl_cat[["table_body"]][["label"]][124]<- "Adj.Tx.(Yes.if.got.any.treatment.for.PDAC).clean"
surv_tbl_cat[["table_body"]][["label"]][130]<- "Recur.(NA.if.non-PDAC.or.non-resectable.disease,.even.if.treated.for.other.causes)"
surv_tbl_cat[["table_body"]][["label"]][23]
surv_tbl_cat[["table_body"]][["label"]][26]
surv_tbl_cat[["table_body"]][["label"]][29]
surv_tbl_cat[["table_body"]][["label"]][97]
surv_tbl_cat[["table_body"]][["label"]][124]
surv_tbl_cat[["table_body"]][["label"]][130]


```


### tbl_survfit()

```{r tbl_survfit}

surv_df <- data.frame()

for (i in 1:seq_along(model_list)){
  surv <- survfit(model_list[[14]])
  sumObj <- surv_summary(surv, data = survDat) 
  df <- attr(sumObj,"table") %>% as_tibble()
  tmp_df <- data.frame(Variable = names(model_list)[[1]], n = df["records",], events = df["events",], median = df["median",], `0.95LCL`= df["0.95LCL",], `0.95UCL`= df["0.95UCL",])
  surv_df <- rbind(surv_df,tmp_df)
}

```


#### Assumptions test

```{r assumptions}

assumption <- list()
for (i in c(1:25,27:45)){
  assum_test <- cox.zph(model_list[[i]])
  assumption [[i]] <-assum_test
}

```

## Save Workbook

```{r workbook}
# Create an Excel workbook
wb <- createWorkbook()

addWorksheet(wb, sheetName = "P-values")
writeDataTable(wb, sheet = 1, x = p_df)

addWorksheet(wb, sheetName = "HR")
writeDataTable(wb, sheet = 2, x = tbl_df)

saveWorkbook(wb, "Survival_Values_final_112623.xlsx")
```

# Chronic Panc vs OS

```{r ChronPancOS}

pdf("/work/users/a/r/arthih/Laura_Clinical_Parsing/ChronicPanc_OS_kmplot.pdf", onefile = F)

km <- with(survDat, Surv(time,event))

p20 = coxph(km ~ chronic_pancreatitis_yn, data = survDat)

bic = round(BIC(p20),3)
hr <- round(1/summary(p20)$coefficients[2],3)
km_fit20 <- survfit(km ~ chronic_pancreatitis_yn, data = survDat, type = "kaplan-meier")
p20 <- ggsurvplot(km_fit20, conf.int = F, pval = T,
                          legend.title="",break.time.by = 12,
                          legend.labs=c("Yes","No"),
                          palette = c("violetred1","turquoise4"),
                          xlab = "Time (months)", risk.table = T,
                          title = paste("YehSeq\nChronic Pancreatitis HR=",hr,
                                        " BIC=",bic,sep=""))
print(p20)

dev.off()
```
